---
title: "Machine Learning - Feature engineering"
output:
  html_document:
    df_print: paged
---

## DefectData Dataset

R package [DefectData](https://github.com/klainfo/DefectData) is a collection of software metrics dataset for software engineering researchers.

### Descriptive Statistics of 6 representative defect datasets

The descriptive statistics are:

-   **System:** name of the dataset.
-   **Corpus:** type of data in the dataset. In this case, all of them are *ck* (chidamber-kemerer metrics).
-   **Defective Ratio:** percentage of total modules that are defective modules.

    $DefectiveModules*100/Modules$
    
-   **Number of Modules:** total modules of the dataset.
-   **Number of Defective Modules:** defective modules of the dataset.
-   **Number of Predictors:** amount of features used in the dataset. In this case, all of them are 20 predictors.
-   **EPV (Events Per Variable):** the number of events (defective modules) divided by the number of predictor variables considered in developing the prediction.

    $DefectiveModules/Predictors$

Six of the 101 datasets available in this github repository have been chosen.

-   *xalan-2.7*: has a high DefectiveRatio and a high number of Modules.
-   *jedit-4.3*: has a low DefectiveRatio and a high number of Modules.
-   *ckjm*: has a medium DefectiveRatio and a low number of Modules.
-   *xalan-2.5*: has a medium DefectiveRatio and a high number of Modules.
-   *forrest-0.6*: has a low DefectiveRatio and a low number of Modules.
-   *pbeans1*: has a low DefectiveRatio and a low number of Modules.

*EPV* is less when *DefectiveModules* is also less and it is larger when *DefectiveModules* is larger.

The following table details the statistics of the chosen datasets:

| System      | Corpus | DefectiveRatio | #Modules | #DefectiveModules | #Predictors | EPV        |
|-----------|-----------|-----------|-----------|-----------|-----------|-----------|
| xalan-2.7   | ck     | 98.789879      | 909      | 898               | 20          | 44.9000000 |
| jedit-4.3   | ck     | 2.235772       | 492      | 11                | 20          | 0.5500000  |
| ckjm        | ck     | 50.000000      | 10       | 5                 | 20          | 0.250000   |
| xalan-2.5   | ck     | 48.194271      | 803      | 387               | 20          | 19.3500000 |
| forrest-0.6 | ck     | 16.666667      | 6        | 1                 | 20          | 0.0500000  |
| pbeans1     | ck     | 76.923077      | 26       | 20                | 20          | 1.0000000  |


### Set up to use

Firstly, we create a list with the names of all chosen datasets.

```{r}
dsnames <- c("xalan-2.7", "jedit-4.3", "ckjm", "xalan-2.5", "forrest-0.6", "pbeans1")
```

The data from the *ckjm* dataset is loaded to show as an example:
```{r}
library(DefectData)

data <- loadData("ckjm")
data$data

# Same in all chosen datasets
data$indep

# Same in all chosen datasets
data$dep
```

Then, we create a function to load only the data from a chosen dataset without indep and dep components. We add this function and *dsnames* list to a R script.

```{r, file = 'loadDataset.R'}
```

Example of *loadDataset* use:
```{r eval=FALSE}
source("./loadDataset.R")
loadDataset("ckjm")
```
